Network Configuration Synthesis with Abstract Topologies

### 2016-11-12 paper/abstraction/paper.tex
more edits

\para{Fault-tolerance policy} This policy specifies how many link failures the network should be able to withstand before connectivity loss for traffic occurs. Operators can  specify different tolerance levels for different pairs of abstract nodes. For instance, they may say that ToR to spine connectivity should be robust to 2 failures, \IE, no ToR-spine pair should lose connectivity as long as the number of simultaneous link failures is 2 or fewer; and ToR-to-ToR connectivity should be be robust to 1 failure.

@@

Instead, we develop a sound analysis based on computing the minimum
number of edge-disjoint policy-compliant paths between pairs of nodes
over abstract topologies. If this number for a pair of nodes is less
than the desired fault-tolerance level, \sysname declares that the
policy cannot be met.  More specifically,
for each abstract role in the network, our analysis will learn facts about the
number of disjoint paths to routers in that role.  For example,
the fact $A_{S}(2,3)$ states that for \emph{all} groups of 2 nodes
in the $S$ (Spine) role, there are 6 disjoint paths to the group---3 
for each of the 2 nodes. A fact such as $S_{S}(2,3)$, states that
\emph{some} group of 2 nodes has the property as opposed to all.
More generally, there is one quantifier ($A$ for all groups
and $S$ for exists a group).  When nodes are nested within pods,
there is one quantifier for each level of the hierarchy, so
$S_P S_{TG} (i,j)$ means that for some pod from the $P$ group of pods
and for some nodes in the $TG$ role within that pod, there exists a
group of $i$ nodes with $j$ paths to each node in the group.

>>>>

\para{Fault-tolerance policy} This policy specifies how many link failures the network should be able to withstand before traffic experiences connectivity loss. Operators can specify different tolerance levels for different pairs of abstract nodes. For instance, they may say that ToR to spine connectivity should be robust to 2 failures, \IE, no ToR-spine pair should lose connectivity as long as the number of simultaneous link failures is 2 or fewer; and ToR-to-ToR connectivity should be be robust to 1 failure.

@@

We develop a sound analysis based on computing the minimum
number of edge-disjoint, policy-compliant paths between pairs of nodes
over abstract topologies. If this number is less
than the desired fault-tolerance level for a pair of nodes, \sysname declares that the
policy cannot be met.  More specifically,
for each abstract role in the network, our analysis will learn facts about the
number of disjoint paths to routers in that role.  For example,
the fact $A_{S}(2,3)$ states that for \emph{all} groups of 2 nodes
in the $S$ (Spine) role, there are 6 disjoint paths to the group---3 
for each of the 2 nodes. A fact such as $S_{S}(2,3)$, states that
\emph{some} group of 2 nodes has the property as opposed to all.
More generally, there is one quantifier ($A$ for all groups
and $S$ for exists a group).  When nodes are nested within pods,
there is one quantifier for each level of the hierarchy, so
$S_P S_{TG} (i,j)$ means that for some pod from the $P$ group of pods
and for some nodes in the $TG$ role within that pod, there exists a
group of $i$ nodes with $j$ paths to each node in the group.
